Glue-on AdS holography for $T\bar T$-deformed CFTs

### 2023-08-28 alpha/GlueonAdS/glueon-poster-v2.tex
Add minor tweaks & update graphics

\preauthor{\par\large\noindent}
\author{
	Luis Apolo,
	Peng-Xiang Hao \textkai{\normalsize 郝鹏翔},
	\textbf{Wen-Xin Lai} \textkai{\small 赖文昕},
	and Wei Song \textkai{\small 宋伟}
}
\postauthor{
	\,\arxiv{2303.04836}
	\par%\vspace{.5\baselineskip}
	\vspace{-.6\baselineskip}
	\noindent\rule{.68\linewidth}{1pt}\par
	\vspace{-.1\baselineskip}
%	\vspace{.3\baselineskip}
}

\predate{\noindent\sffamily\,%
	Yau Mathematical Sciences Center YMSC, Tsinghua
	---
}
\date{September 2023}
\postdate{
	@ YITP, Kyoto
%	\vspace{0\baselineskip}
}

@@

\noindent%
\textbf{Abstract:}

@@

\textbf{Pure Einstein gravity} without matter in $\mrm{AdS}_3$:
\begin{equation}
\hspace{-2.5em}
\begin{aligned}
	ds^2
	&= \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg)\\
	&= n_\mu n_\nu dx^\mu dx^\nu + \frac{1}{\zeta} \gamma_{ij}dx^i dx^j,\quad
\end{aligned}
\label{fggauge}
\end{equation}

\begin{itemize}
\item Transverse coordinates: $x^{i} \sim \varphi, t$ \\
	Lightcone coordinates: $u,v = \varphi \pm t$

	$\mathcal L(u), \bar{\mathcal L}(v)$: arbitrary periodic functions
\item Radial coordinate: $
	\ell^{-2} g_{\varphi\varphi} \equiv r^2 \equiv \frac{1}{\zeta}$\\
	$r$: the ``proper radius''
\end{itemize}
\begin{center}
	\vspace{-.5\baselineskip}
	\includegraphics[width=.52\linewidth]{img/foliation.pdf}

@@

	\vspace{-.5\baselineskip}
\end{center}
\begin{itemize}
\item Structure: foliated by constant $\zeta$ surfaces ${\mathcal N}_\zeta$\\[.7ex]
Asymptotic boundary: $\mcal{N}_0$ is at $\zeta \to 0$
\\[1ex]
\citations{%
	\textcite{Fefferman:2007rka}\\
	\textcite{Banados:1992wn}%\\
%	\textcite{Banados:1998gg}
}
\end{itemize}

\textbf{``\,$\TTbar$\,'' deformation} as the flow of action:
\begin{align}
\hspace{-1.5em}
	\partial_{\sidenote{\mu}} I &= {8 \pi} \int d^2x \, T\bar T_{(\sidenote{\mu})} = {\pi} \int d^2x\,\big( T^{ij}T_{ij}- (T^i_i)^2 \big)_{(\sidenote{\mu})},\notag\\
	&x, \bar{x} = \varphi' \pm t'
	\label{TTbardef}
\end{align}

@@

\vspace{-.5\baselineskip}

@@

\subsection*{Cutoff $\mrm{AdS}_3$ duality:\texstringonly{\\} Holography within a finite Dirichlet wall}

\citations{
\textcite{McGough:2016lol}\\
\textcite{Kraus:2018xrn} \textit{et al}
}

@@

\vspace*{-4\baselineskip}
\begin{center}
	\mbox{
		\hspace{-2.6em}
		\includegraphics[width=1.17\linewidth]{img/ads-cft-cutoff.png}
	}

	\vspace{-.9\baselineskip}\small
	Cutoff $\mrm{AdS}_3$\,/\,\TTbar-deformed $\mrm{CFT}_2$

@@

\parbox{\linewidth}{
\vspace{-\baselineskip}
\textbf{\begin{equation*}
\hspace{-3em}
\begin{aligned}
	\textrm{Cutoff}
	\ &/\ %
	\text{\textit{glue-on} $\mrm{AdS}_3$ Gravity}
	\!\!&\equiv\ %
	\textrm{\TTbar deformed $\mrm{CFT}_2$ at $\mcal{N}_{\zeta_c}$} \\
	\zeta_c > 0
	\ &/\ %
	\zeta_c < 0
	& \mu \in \mbb{R}\hspace{1em}\,
\end{aligned}
\end{equation*}}
\begin{center}
	\vspace{-1\baselineskip}%
	\centering
	\includegraphics[width=.7\linewidth]{img/diagram.pdf}

@@

	\item \textbf{\textit{State-dependent} maps of \mbox{coordinates}}
	\begin{align}
		dt' &= \sqrt{ \big(1 - \zeta_c (T_u+T_v)^2 \big) \big(1 - \zeta_c (T_u-T_v)^2 \big) } \, dt, \notag \\
		 d\varphi' &= d\varphi + \zeta_c \big( T_u^2 - T_v^2 \big)\,dt.
	\label{eq:state_dependent_map}
	\end{align}
	$\leadsto$ correct charges, the modified signal propagation speed $v'_{\pm} \equiv \pm {d\varphi'}/{dt'}$, and \TTbar \textbf{thermodynamics} upon Wick rotation. In particular,
	\begin{equation*}
	\hspace{-.5em} \mu > 0,\ \ \,
		T_L(\mu)\,T_R(\mu) \le - \frac{1}{4\pi^2 \ell^2 \zeta_c} = \frac{3}{4\pi^2c\mu} = T_H(\mu)^2.
	\end{equation*}
	$T_{L,R}$: temperatures associated with $u',v' = \varphi' \pm t'$.\\
	$T_H$: the \textit{Hagedorn temperature}: exceeding $T_H$ leads to a complex entropy.

@@

\item \textbf{Torus:} {modular invariance} \& sparseness of the ``light'' spectrum at large $c$ $\leadsto$ universal form:
	\begin{equation*}\small
	\hspace{-2em}
		\log   Z_{T\bar T}(\mu)  \approx \left\{ \begin{aligned}
		& {-\frac{1}{2}}\,(\beta_L + \beta_R)\, RE_{\text{vac}}(\mu),  &\beta_L \beta_R > 1, \\
		& {-2 \pi^2 \bigg(\frac{1}{\beta_L} + \frac{1}{\beta_R}\bigg)  RE_{\text{vac}}\bigg(\frac{4\pi^2}{\beta_L \beta_R} \mu \bigg)},  &\beta_L\beta_R < 1. %\\[2ex]
		 \end{aligned} \right. %\label{ZTTbar}
	\end{equation*}
	\begin{flushright}
		\vspace{-.5\baselineskip}
		\citations{\noindent%
			\textcite{Datta:2018thy}\\
			\textcite{Apolo:2023aho}\\
			cf.~\textcite{Hartman:2014oaa}
		}
		\vspace{-.5\baselineskip}
	\end{flushright}

@@

\hfill\mbox{\footnotesize \textcite{Donnelly:2018bef}}
	\begin{equation}
%		\label{sphere:stresstensor}
		\langle T_{ij}\rangle = -\frac{1}{4\pi\mu} \bigg(1-\sqrt{1-\frac{c\mu}{3R^2}}\, \bigg)  \gamma_{ij}.
	\end{equation}
Trace relation: \mbox{$
%	\begin{align*}
%\partial_\mu \log Z_{\TTbar}(\mu)&=8\pi \int d^2x\sqrt{\gamma}\, \langle T\bar{T} \rangle \\
(-R)\,\partial_R \log Z_{\TTbar}(\mu)=\int d^2x\sqrt{\gamma}\,\langle T^i_i \rangle
%	\end{align*}
$} and the flow equation \eqref{TTbardef} 
admit the general \mbox{solution} with a $\mu$-\textit{independent} integration constant $a$:
	\begin{equation*}\small
	\hspace{-1.3em}
		\log Z_{\TTbar}(\mu, a) = \tfrac{c}{3} \log \Big[\tfrac{R}{a}   \Big(1+\sqrt{1-\tfrac{c \mu }{3  R^2}}\, \Big) \Big] - \tfrac{R^2}{\mu}  \sqrt{1-\tfrac{c \mu }{3 R^2}} + \tfrac{R^2}{\mu}. %\label{Zsol}
	\end{equation*}
	\begin{itemize}%[noitemsep]
	\item $a = \sqrt{c|\mu|/3}$: \mbox{recover {\small
		\textsl{\citeauthor{Donnelly:2018bef}}
		\cite{Donnelly:2018bef}
	}} \\
	$a = \epsilon$: also a valid choice, where the the RG length scale $\epsilon$ is decoupled from $\mu$.

@@

\hspace{-.7em}
\begin{minipage}[c]{.81\linewidth}
\begin{itemize}[noitemsep,leftmargin=5em]\small
\item[\texttt{Email:}]
	\url{bryanlais@gmail.com}
\item[\texttt{Inspire:}]
	\href{https://inspirehep.net/authors/2640135}{
		\texttt{inspirehep.net/authors/2640135}
	}
\item[\texttt{GitHub:}]
	\href{https://github.com/bryango}{
		\texttt{github.com/bryango}
	}
\end{itemize}
\end{minipage}%
\hfill%
\begin{minipage}{.17\linewidth}
\includegraphics[width=\linewidth]{img/inspire-qr.png}
\end{minipage}%
~\mbox{}

>>>>

\preauthor{\par\large\noindent}
\author{%
	Luis Apolo,
	Peng-Xiang Hao \textkai{\normalsize 郝鹏翔},
	\textbf{Wen-Xin Lai \textkai{\small 赖文昕}},
	and Wei Song \textkai{\small 宋伟}
}
\postauthor{
	\,\arxiv{2303.04836}
	\par%\vspace{.5\baselineskip}
	\vspace{-.6\baselineskip}
	\noindent\rule{.68\linewidth}{1pt}\par
	\vspace{-.1\baselineskip}
%	\vspace{.3\baselineskip}
}

\predate{\noindent\sffamily%
	\begin{minipage}{3em}
		\includegraphics[width=2.7em]{img/ymsc-logo.pdf}
	\end{minipage}
	Yau Mathematical Sciences Center YMSC, Tsinghua
	---
}
\date{September 2023}
\postdate{
	@ YITP, Kyoto
%	\vspace{0\baselineskip}
}

@@

%\textbf{Abstract:}
\,\\[-2.2\baselineskip]

@@

\textbf{Pure Einstein gravity} without matter in $\mrm{AdS}_3$:
\begin{align}
\hspace{-.8em}
	ds^2
	&= \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg) \notag\\
	&= n_\mu n_\nu dx^\mu dx^\nu + \frac{1}{\zeta} \gamma_{ij}dx^i dx^j, \label{fggauge}
\end{align}

\begin{itemize}
\item Transverse coordinates: $x^{i} \sim \varphi, t$ \\
	Light-cone coordinates: $u,v = \varphi \pm t$

	$\mathcal L(u), \bar{\mathcal L}(v)$: arbitrary periodic functions
\item Radial coordinate: $
	\ell^{-2} g_{\varphi\varphi} \equiv r^2 \equiv \zeta^{-1}$\\
	$r$: the ``proper radius''
\end{itemize}
\begin{center}
	\vspace{-.5\baselineskip}
	\includegraphics[width=.52\linewidth]{img/foliation.pdf}

@@

	\vspace{-.5\baselineskip}
\end{center}
\begin{itemize}
\item Structure: foliated by constant $\zeta$ surfaces ${\mathcal N}_\zeta$\\[.6ex]
Asymptotic boundary: $\mcal{N}_0$ is at $\zeta \to 0$
\\[1ex]
\citations{%
	\textcite{Fefferman:2007rka}\\
	\textcite{Banados:1992wn}%\\
%	\textcite{Banados:1998gg}
}
\end{itemize}

\textbf{``$\thinmspace[.9]\TTbar$\,'' deformation} as the flow of action:
\begin{align}
\hspace{-.1em}
	\partial_{\sidenote{\mu}} I &= {8 \pi} \int d^2x \, T\bar T_{(\sidenote{\mu})} = {\pi} \int d^2x\,\big( T^{ij}T_{ij}- (T^i_i)^2 \big)_{(\sidenote{\mu})},\notag\\
	&x, \bar{x} = \varphi' \pm t'
	\label{TTbardef}
\end{align}

@@

\vspace{-.8\baselineskip}

@@

\subsection*{Cutoff $\mrm{AdS}_3$ duality:\texstringonly{\\} Holography within a finite Dirichlet wall}
\vspace{-.2\baselineskip}
\citations{
\textcite{McGough:2016lol}\\
\textcite{Kraus:2018xrn} \textit{et al}
}

@@

\vspace*{-3.6\baselineskip}
\begin{center}
	\mbox{
		\hspace{-1.55em}
		\includegraphics[width=1.14\linewidth]{img/ads-cft-cutoff.png}
	}

	\vspace{-.8\baselineskip}\small
	Cutoff $\mrm{AdS}_3$\,/\,\TTbar-deformed $\mrm{CFT}_2$

@@

\parbox{\linewidth}{
\vspace{-\baselineskip}
\textbf{\begin{equation*}
\hspace{-2.8em}
\begin{aligned}
	\textrm{Cutoff}
	\ &/\ %
	\text{\textit{glue-on} $\mrm{AdS}_3$ Gravity}
	\!\!&\equiv\ %
	\textrm{\TTbar deformed $\mrm{CFT}_2$ at $\mcal{N}_{\zeta_c}$} \\
	\zeta_c > 0
	\ &/\ %
	\zeta_c < 0
	& \mu \in \mbb{R}\hspace{1em}\,
\end{aligned}
\end{equation*}}
\begin{center}
	\vspace{-1\baselineskip}%
	\centering
	\includegraphics[width=.7\linewidth]{img/diagram.pdf}

@@

	\item \textbf{\textit{State-dependent} maps of \mbox{coordinates}:}
	\begin{align}
		dt' &= \sqrt{ \big(1 - \zeta_c (T_u+T_v)^2 \big) \big(1 - \zeta_c (T_u-T_v)^2 \big) } \, dt, \notag \\
		 d\varphi' &= d\varphi + \zeta_c \big( T_u^2 - T_v^2 \big)\,dt.
	\label{eq:state_dependent_map}
	\end{align}
	$\leadsto$ correct charges, the modified signal propagation speed $v'_{\pm} \equiv \pm {d\varphi'}/{dt'}$, and \TTbar \textbf{thermodynamics} upon Wick rotation. In particular,
	\begin{equation*}
	\hspace{-.5em} \mu > 0,\ \ \,
		T_L(\mu)\,T_R(\mu) \le - \frac{1}{4\pi^2 \ell^2 \zeta_c} = \frac{3}{4\pi^2c\mu} = T_H(\mu)^2.
	\end{equation*}
	$T_{L,R}$: temperatures associated with $u',v' = \varphi' \pm t'$.\\
	$T_H$: the \textit{Hagedorn temperature}: exceeding $T_H$ leads to a complex entropy.

@@

\item \textbf{Torus:} {modular invariance} \& sparseness of the ``light'' spectrum at large $c$ $\leadsto$ universal form:
	\begin{equation*}\small
	\hspace{-2.3em}
		\log   Z_{T\bar T}(\mu)  \approx \left\{ \begin{aligned}
		& {-\frac{1}{2}}\,(\beta_L + \beta_R)\, RE_{\text{vac}}(\mu),  &\beta_L \beta_R > 1, \\
		& {-2 \pi^2 \bigg(\frac{1}{\beta_L} + \frac{1}{\beta_R}\bigg)  RE_{\text{vac}}\bigg(\frac{4\pi^2}{\beta_L \beta_R} \mu \bigg)},  &\beta_L\beta_R < 1. %\\[2ex]
		 \end{aligned} \right. %\label{ZTTbar}
	\end{equation*}
	\begin{flushright}
		\vspace{-.5\baselineskip}
		\citations{\noindent%
			\textcite{Datta:2018thy}\\
			\textcite{Apolo:2023aho}\\
			cf.~\textcite{Hartman:2014oaa}
		}
		\vspace{-.5\baselineskip}
	\end{flushright}

@@

\hfill\mbox{\footnotesize \textcite{Donnelly:2018bef}}
	\begin{equation}
%		\label{sphere:stresstensor}
		\langle T_{ij}\rangle = -\frac{1}{4\pi\mu} \bigg(1-\sqrt{1-\frac{c\mu}{3R^2}}\, \bigg)  \gamma_{ij}.
	\end{equation}
Trace relation: \mbox{$
%	\begin{align*}
%\partial_\mu \log Z_{\TTbar}(\mu)&=8\pi \int d^2x\sqrt{\gamma}\, \langle T\bar{T} \rangle \\
(-R)\,\partial_R \log Z_{\TTbar}(\mu)=\int d^2x\sqrt{\gamma}\,\langle T^i_i \rangle
%	\end{align*}
$} and the flow equation \eqref{TTbardef} 
admit the general \mbox{solution} with a $\mu$-\textit{independent} integration constant $a$:
	\begin{equation*}\small
	\hspace{-1.6em}
		\log Z_{\TTbar}(\mu, a) = \tfrac{c}{3} \log \Big[\tfrac{R}{a}   \Big(1+\sqrt{1-\tfrac{c \mu }{3  R^2}}\, \Big) \Big] - \tfrac{R^2}{\mu}  \sqrt{1-\tfrac{c \mu }{3 R^2}} + \tfrac{R^2}{\mu}. %\label{Zsol}
	\end{equation*}
	\begin{itemize}%[noitemsep]
	\item $a = \sqrt{c|\mu|/3}$: \mbox{recover {\small
		\textsl{\citeauthor{Donnelly:2018bef}}
		\cite{Donnelly:2018bef}
	}} \\
	$a = \epsilon$: also a valid choice, where the RG length scale $\epsilon$ is decoupled from $\mu$.

@@

\hspace{-.7em}
\begin{minipage}[c]{.81\linewidth}
\begin{itemize}[noitemsep,leftmargin=5em]\small
\item[\texttt{Email:}]
	\url{bryanlais@gmail.com}
\item[\texttt{Inspire:}]
	\href{https://inspirehep.net/authors/2640135}{
		\texttt{inspirehep.net/authors/2640135}
	}
\item[\texttt{GitHub:}]
	\href{https://github.com/bryango}{
		\texttt{github.com/bryango}
	}
\end{itemize}
\end{minipage}%
\hfill%
\begin{minipage}{.17\linewidth}
\includegraphics[width=\linewidth]{img/inspire-qr-cy.png}
\end{minipage}%
~\mbox{}
